Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
combine block ordering items, todo on saint-donat

\noindent
with multiplication structure corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X \cong \proj R$. When $g \geq 2$, Petri's
theorem gives generators and relations for $R(X, K_X)$ showing that
in most cases $R(X, K_X)$ is generated in degree 1 with relations
in degree 2 (one demonstration is given by Saint-Donat\cite[p. 157]{saint-donat:proj}). This has the
pleasant geometric consequence that all such canonically embedded
curves are scheme theoretically cut out by quadratic equations.

@@

\todo{State for even weight modular forms attributed to VZB.}
\begin{thm}
\label{thm:main}
Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere? No, use seperable stacky points} so
that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
log spin canonical ring

@@

In the \textbf{(graded) block} (or \textbf{elimination}) term
ordering on $k[x_{d_1, 1}, \ldots, x_{d_n, n}] \otimes k[y_{d_1', 1},
\ldots, y_{d_m', m}]$, we define $\alpha \succ \beta$ if
  \begin{enumerate}
	\item[(i)] $\deg \alpha  > \deg \beta$ or
  \item[(ii)] $\deg \alpha = \deg \beta$ and 
    \begin{enumerate}
    \item $\alpha_y \succ_y \beta_y$ or
    \item $\alpha_y = \beta_y$ and $\alpha_x \succ_x \beta_x$
    \end{enumerate}
  \end{enumerate}
\end{defn}

>>>>

\noindent
with multiplication structure corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X \cong \proj R$. When $g \geq 2$, Petri's
theorem gives generators and relations for $R(X, K_X)$ showing that
in most cases $R(X, K_X)$ is generated in degree 1 with relations
in degree 2 (one demonstration is given by Saint-Donat\cite[p. 157]
{saint-donat:proj}). This has the pleasant geometric consequence \todo{maybe use a different ref}
that all such canonically embedded curves are scheme theoretically 
cut out by quadratic equations.

@@

\todo{State for even weight modular forms attributed to VZB.}
\begin{thm}
\label{thm:main}
Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere? No, use separable stacky points} so
that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
log spin canonical ring

@@

In the \textbf{(graded) block} (or \textbf{elimination}) term
ordering on $k[x_{d_1, 1}, \ldots, x_{d_n, n}] \otimes k[y_{d_1', 1},
\ldots, y_{d_m', m}]$, we define $\alpha \succ \beta$ if
  \begin{enumerate}
	\item[(i)] $\deg \alpha  > \deg \beta$ or
  \item[(ii)] $\deg \alpha = \deg \beta$ and $\alpha_y \succ_y \beta_y$ or
	\item[(iii)] $\deg \alpha = \deg \beta$ and $\alpha_y = \beta_y$ and $\alpha_x \succ_x \beta_x$
  \end{enumerate}
\end{defn}
